DATA 621 - Business Analytics and Data Mining

### 2020-12-03 Final_project/Final Project Paper - Group 2.Rmd
More fixes, restor unam

colClass <- c(rep('character', 4L), 'integer', 'POSIXct', 'character',
              rep('double', 4L), rep('boolean', 3L))
us_set <- fread(us_path, encoding = 'UTF-8', colClasses = colClass)
nobsUS <- nrow(us_set)

@@

# Change data types for convenience, add target bucket, count tags and then
# get rid of actual tags and category IDs

@@

A feature that we will also consider is `lkratio`: the ratio of likes to
dislikes. This will help ascertain if it is the magnitude or the preponderance
which has a greater effect. As there may be some rare videos with no dislikes,
the ratios will be set to 1.

```{r addFeatures}
usExtract[, lkratio := ifelse(dislikes == 0, 1, likes / dislikes)]

modDum <- dummyVars(views ~ likes + dislikes + comments + tags + category +
                   comments_disabled + ratings_disabled +
                   video_error_or_removed + lkratio,
                   data = usExtract, fullRank = TRUE)
modMat <- predict(modDum, usExtract)
```

## Model Building
We will first separate 20% of the data as a true holdout set. It is on this data
that our models will be compared. We will train models on the remaining 80% of
the data.

@@

The signs of these coefficients make sense in the main. Increased `likes`,
`dislikes` are correlated with increased views. Of course one usually views a
video at least once prior to rating it. Increased `comments` is negatively
correlated with views.

We set the baseline category to `Entertainment`, considering it was the most
popular. Therefore we expected negative coefficients for other categories. We
were surprised that was not the case. The "worst" category predictor by
magnitude is the `Nonprofits & Activism`. The "best" is `Gaming`.

@@

## Findings

>>>>

colClass <- c(rep('character', 4L), 'integer', 'POSIXct', 'character',
              rep('double', 4L), rep('logical', 3L))
us_set <- fread(us_path, encoding = 'UTF-8', colClasses = colClass)
nobsUS <- nrow(us_set)

@@

# Change data types for convenience, add target bucket, count tags and then get
# rid of actual tags and category IDs

@@

A feature that we will also consider is `lkratio`: the ratio of likes to
dislikes. This will help ascertain if it is the magnitude or the preponderance
which has a greater effect. As there may be some rare videos with no dislikes,
the ratios will be set to 1. The variable `unan`, short for unanimous, will
reflect that some videos have likes but no dislikes, to balance the ratio of 1
which should have been `NaN`, a division by 0 error.

```{r addFeatures}
usExtract[, `:=`(lkratio = ifelse(dislikes == 0, 1, likes / dislikes),
                 unan = ifelse(dislikes == 0 & likes > 0, TRUE, FALSE))]

modDum <- dummyVars(views ~ likes + dislikes + comments + tags + category +
                   comments_disabled + ratings_disabled +
                   video_error_or_removed + lkratio + unan,
                   data = usExtract, fullRank = TRUE)
modMat <- predict(modDum, usExtract)
```

## Model Building & Interpretation
We will first separate 20% of the data as a true holdout set. It is on this data
that our models will be compared. We will train models on the remaining 80% of
the data.

@@

The signs of these coefficients make sense in the main. Increased `likes` and
`dislikes` are correlated with increased views. Of course one usually views a
video at least once prior to rating it. Increased `comments` is negatively
correlated with views.

We set the baseline category to `Entertainment`, considering it was the most
popular. Therefore we expected negative coefficients for other categories found
significant. We were surprised that `Film & Animation` was an exception. The
"worst" category predictor by magnitude is the `Nonprofits & Activism`.

@@
